\documentclass[11pt, titlepage]{article}
\usepackage[pdftex]{graphicx}
\usepackage{mathtools}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{microtype}
\usepackage{parskip}
\makeatletter
\renewcommand\@seccntformat[1]{}
\makeatother

\author{Graeme Douglas (76316090)}

\begin{document}

\section{Requirements}
\subsection{Functional Requirements}
\begin{enumerate}
\item The system must identify products given a set of descriptive
identifier words.
\\ Priority: High - Estimate: 10 hours
\item The system should allow administrators to configure which words identify
a product.
\\ Priority: High - Estimate: 4 hours
\item The system shall ask users questions to help identify
products sold, as necessary.
\\ Priority: High - Estimate: 3 hours
\item The system should store all configuration options in a database.
\\ Priority: High - Estimate: 2 hours
\item The system should provide the user with a way to choose one or more
products from a list after the user has given all the information for the
product that she can think of.
\\ Priority: High - Estimate: 1 hour
\item The system should allow identified items to be added to an order.
\\ Priority: High - Estimate: 1 hour
\item The system should be able to respond to erroneous or otherwise ambiguous
user input appropriately.
\\ Priority: High - Estimate: 1 hour
\item The system should allow the user to place an order.
\\ Priority: Medium - Estimate: 3 hours
\item The system should allow administrators to configure which words are
associated with a given action.
\\ Priority: Medium - Estimate: 3 hours
\item The system should have a configuration page that administrators can use
to manage all of the system's configurables.
\\ Priority: Medium - Estimate: 2 hours
\item The system should allow administrators to configure what questions the
system should ask in order to identify a product.
\\ Priority: Medium - Estimate: 2 hours
\item The system should alert the user to confirm when an order has been placed.
\\ Priority: Low - Estimate: 1 hour
\end{enumerate}
\subsection{Non-functional Requirements}
\begin{enumerate}
\item The system should interact with the user in a natural, conversational
manner.
\\ Priority: High - Estimate: 3 hours
\item The system shall allow the user to chat with the system via a web page.
\\ Priority: High - Estimate: 2 hours
\item The system must be able to carry conversations continuously without page
refreshes.
\\ Priority: High - Estimate: 1 hour
\item The system must be able to respond a customer within 3 seconds of the
message being received.
\\ Priority: High - Estimate: Duration of project
\item The system should email users to do order confirmation.
\\ Priority: Low - Estimate: 1 hour
\end{enumerate}
\subsection{Environmental Constraints}
\begin{enumerate}
\item The system's chat client must be language independent.
\\ Priority: High - Estimate: N/A (Will be by design)
\end{enumerate}

\end{document}

